%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Rakshith G} \\ \vspace{1pt}
    Machine Learning Software Development Engineer \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\  \underline{+91 9731429857} ~ \href{mailto:rakshithg2098@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rakshithg2098@gmail.com}} ~
    \href{https://www.linkedin.com/in/rakshithg98/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/rakshithg98}}  ~
    \href{https://github.com/rakshithGGowda}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/rakshithGGowda}}
    \vspace{-2pt}
\end{center}


%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      ML Engineer with 3 years at Mercedes-Benz R\&D, specializing in generative AI, Vision-Language models, and end-to-end MLOps. Key contributions include a patent-pending 3D MeshGAN, Automated AGV Robotic Warehouse, Package Space Optimization.
    }}
  \end{itemize}
  \vspace{-16pt}


%-----------SKILLS-----------
\section{Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \footnotesize{\item{
      \setlength{\itemsep}{5pt}
      \textbf{Languages}{: Python, JavaScript, C++} \\[5pt]
      \textbf{Deep Learning}{: PyTorch, TensorFlow, Keras, Scikit-learn, Hugging Face Ecosystem} \\[5pt]
      \textbf{Computer Vision}{: Multimodal Vision-Language Models, Object Detection, Pose Estimation, GANs (C-GANs), MeshGAN} \\[4pt]
      \textbf{Natural Language Processing:}{: LLM Fine-Tuning, RAG Systems, Auto-Encoders, Transformers, Tokenization, Agentic Workflows} \\[5pt]
      \textbf{Backend and MLOps}{: Docker, Docker-Compose, FastAPI, Flask, GCP, AWS, MLflow, GitHub Actions} \\[5pt]
      \textbf{Data Visualization}{: Matplotlib, Seaborn, Plotly, TensorBoard, Tableau} \\[5pt]
      \textbf{Cloud Technologies:}{: AWS, Google Cloud Platform, Firebase, Hugging Face Spaces} \\[5pt]
      \textbf{Tools and Workflow:}{: REST APIs, SQLAlchemy, Streamlit, Linux, Agile/Scrum} \\
    }}
  \end{itemize}
  \vspace{-16pt}

    \vspace{5pt}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mercedes-Benz Research and Development India}{2 Years}
      {Machine Learning Engineer}{Oct 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Architected the \textbf{Process Code tracking system} (27 codes across 3 customers) with DB migrations, FK constraints, and rule-engine integration — enabling full traceability of forklift placement decisions across 10+ business rules.}
        \resumeItem{Built a \textbf{Spatial Optimiser} algorithm that minimises AGV forklift movements by exchanging items between impure stacking towers, reducing unnecessary warehouse traversals for robotic operations.}
        \resumeItem{Developed \textbf{Post-Simulation position optimisation} for short towers on Pre-Stacking Areas, combining and repositioning items to maximise container space utilisation for autonomous forklift placement.}
        \resumeItem{Implemented \textbf{Machine Vision integration} pipeline processing real-time 3D dimension measurements from cameras, updating item dimensions with comparison history and triggering re-stacking logic.}
        \resumeItem{Designed \textbf{PHI UI E2E automation framework} using Playwright to simulate forklift driver workflows (login, scan, placement) — replacing manual testing of the distributed microservices system.}
        \resumeItem{Contributed to \textbf{Randomised Greedy 3D bin-packing solver} with multiple RS/sorting strategies, population-based optimisation, and rotation handling for containerised freight loading.}
        \\
    \resumeItemListEnd

    \resumeSubheading
      {Publicis Sapient}{1.8 Years}
      {Software Development Engineer L1}{Jan 2021 -- Nov 2021}
      \resumeItemListStart
        \resumeItem{Enhanced Web UI for Automotive Company Improved page speed by 30\%, and increased customer retention by 10\%.}
        \resumeItem{Implemented Real-Time Features Introduced online booking for test drives, home delivery, owner services.}
        \resumeItem{Agile Development and Cross-Skills Achievement: Leveraged Agile methodology and advanced analytics for improved user experience; recognized for participation in the Cross Skills Program and embodying core company values.}
        \\
      \resumeItemListEnd
    \vspace{-15pt}
    \resumeSubheading
        {}{}
        {Quality Engineer L1}{Jun 2020 - Jan 2021}
        \resumeItemListStart
        \resumeItem{Conducted UI web automation testing for a in the Automotive Industry, utilizing the Watir (Ruby) library in Blunder and associating with CICD (Continuous Integration and Continuous Deployment) using Jenkins }
        \resumeItem{Performed Cross-browser and Responsive devices UI/UX testing using BrowserStack.}
        \resumeItem{Worked on CMS tool: Adobe Experience Manager (AEM) for authoring and testing purposes.}
        % \resumeItem{Conducted API testing using Postman.}
        \\
         \resumeItemListEnd
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

\vspace{5pt}
%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
         \resumeProjectHeading
            {\textbf{Real-Time Indian Sign Language Classification using LSTM} $|$ \emph{Machine Learning}}{Mar 2023}
          \resumeItemListStart
        \resumeItem{Curated 3000 ISL gesture videos using MediaPipe Holistic for "Help me," "Call police," and "Thank you."}
        \resumeItem{Engineered a preprocessing pipeline, normalizing keypoints and segmenting features.}
        \resumeItem{Designed a three-layer LSTM model for precise ISL gesture recognition, achieving 92.5\% accuracy.}
          \resumeItemListEnd
          \vspace{-17pt}
            \resumeProjectHeading
                {\textbf{Automated Real-Time Accident Detection System } $|$ \emph{Computer Vision}}{In Progress}
          \resumeItemListStart
            \resumeItem{Created a realtime accident detection system with computer vision, YoloV7 Transfer Learning, RAFT for Optical Flow.}
            \resumeItem{Envisioned to enhance road safety by reducing emergency response times and improving resource allocation.}
            \resumeItem{Implementing innovative technologies to identify vehicles, pedestrians, and road elements in live video and trigger alerts.}
          \resumeItemListEnd
          \vspace{-10pt}
          % \resumeProjectHeading
          % {\textbf{Image Denoising using Autoencoders} $|$ \emph{Deep Learning}}{February 2023}
          % \resumeItemListStart
          %   % \resumeItem{Executed an academic project on image denoising with autoencoders, leveraging deep learning principles.}
          %   \resumeItem{Developed a robust autoencoder architecture, integrating encoder and decoder components for noise reduction.}
          %   \resumeItem{Engineered a specialized dataset containing clean and noisy images, crucial for training the autoencoder effectively.}
          %   % \resumeItem{Applied a loss function to refine the autoencoder's training process, enhancing its noise reduction capabilities.}
          %   \resumeItem{Translated theoretical concepts into practical implementation using TensorFlow and Keras, showcasing the complete workflow of creating, training, and utilizing the autoencoder for image denoising.}
          % \resumeItemListEnd

           \vspace{35pt}
            \resumeProjectHeading
          {\textbf{Satellite Image to Maps Translation using pix2pix GAN} $|$ \emph{Computer Vision}}{Nov 2022}
          \resumeItemListStart
            \resumeItem{Implemented pix2pix GAN with U-Net generator for satellite image to maps translation.}
            \resumeItem{Utilized conditional adversarial network follows Image-to-Image Translation with Conditional Adversarial Networks.}
            \resumeItem{Led innovative image translation with learned mappings, marking a paradigm shift in automation.}
          \resumeItemListEnd
          \vspace{-20pt}
            \resumeProjectHeading
          {\textbf{Deep Learning for Age Estimation using Facial Images} $|$ \emph{ACIT Conference 2020 | IACIT-20-600}}{Jan 2020}
          \resumeItemListStart
            % \resumeItem{Addressed the critical role of age identification in user verification for applications and websites age-restricted content.}
            \resumeItem{Employed Deep Convolutional Neural Networks to enhance age and gender prediction, surpasses traditional algorithms.}
            \resumeItem{Built a TensorFlow Lite model for age prediction, integrated into an Android app to regulate child internet access.}
            % \resumeItem{Leveraged a vast dataset of 500,000+ face images from IMDB and WIKI databases to surpass existing limitations.}
            \resumeItem{Published a scientific paper at ACIT 2020 (Paper ID: IACIT-20-600), showcasing project research and contributions.}
          \resumeItemListEnd
          \vspace{-20pt}
               \resumeProjectHeading
            {\textbf{Responsive Movie Information Website} $|$ \emph{JavaScript, CSS, HTML - \href{https://movies-info12.netlify.app/}{\underline{View Website}} \href{https://github.com/rakshithGGowda/web-dev-movies}{\underline{GitHub Code}}}}{Dec 2020}
          \resumeItemListStart
            \resumeItem{Designed responsive Movie Information website with Popular and Upcoming movie sections.}
            \resumeItem{Used Vanilla JavaScript for dynamic UI and smooth animations, improving user experience.}
            \resumeItem{Integrated front-end with back-end API links for seamless movie detail display.}
          \resumeItemListEnd
          \vspace{-20pt}
          \resumeProjectHeading
          {\textbf{E-commerce Website Development} $|$ \emph{ReactJs JavaScript, CSS, HTML - \href{https://computersry.netlify.app/}{\underline{View Website}} \href{https://github.com/rakshithGGowda/Computersry}{\underline{GitHub Code}}}}{Sep 2021}
          \resumeItemListStart
            \resumeItem{Developed a End-to-End E-commerce platform using ReactJS Libraries, featuring modern design and animations.}
            \resumeItem{Enabled on-the-go product management via Sanity and achieved complete Stripe integration for real payments.}
            \resumeItem{advanced cart, checkout functionalities, and enriched user experience through interactive design.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, JavaScript,TypeScript, C, HTML/CSS, SQL} \\
     \textbf{Developer Tools}{: VS Code, Git, GitHub/GitLab/Bitbucket, AnaConda, LATEX} \\
     \textbf{Technologies/Frameworks}{: ReactJs, Numpy, Scikit-Learn, PyTorch, TensorFlow } \\
    }}
 \end{itemize}


%-----------INVOLVEMENT---------------
\section{Leadership/Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{National Institute of Technology Karnataka}{Spring 2023 -- Present}{Placement Coordinator}{}
            \resumeItemListStart
                \resumeItem{Leading career placements, forging strong industry alliances as NITK's Placement Coordinator.}
                \resumeItem{Strengthened networking prospects by engaging alumni, fostering mentorship to promote impactful talent growth.}
                \resumeItem{Provided personalized guidance, organized events, and managed databases to boost student support and industry colab.    }
            \resumeItemListEnd
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
        \resumeSubheading{}{}{Internship Coordinator}{Aug 2022 - May 2023}
            \resumeItemListStart
                \resumeItem{Internship Program Lead: Designed and managed transformative industry internships, fostering student growth.}
                \resumeItem{Guidance \& Empowerment: Mentored and supported students for successful internships and career development.}
                \resumeItem{Administrative Excellence: Orchestrated orientations, evaluations, and database management for seamless internship.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
        \vspace{-30pt}
        \resumeSubHeadingListStart
        \resumeSubheading{}{}{Class Representative | B.Tech | REVA University}{Aug 2016 - Aug 2020}
            \resumeItemListStart
                \resumeItem{Effectively coordinated activities, Championing student interests for an interactive learning journey.  }
                \resumeItem{\textbf{Volunteered as an Event Organizer} for Reva Research Conclave (RRC-2018).}
                \resumeItem{Led as a Team \textbf{Captain} for the football team during my B.Tech.}
                \\
                \vspace{3pt}
                \textbf{Skills:} Communication  · Management  · People skill · Interpersonal Skills · Leadership
            \resumeItemListEnd
    \resumeSubHeadingListEnd

            \vspace{-19pt}
        \resumeSubHeadingListStart
        \resumeSubheading{Achievements/Awards }{}{}{}
        \vspace{-17pt}
            \resumeItemListStart
                \resumeItem{Secured All India Rank of \textbf{2031} in \textbf{GATE 2022} among 120 thousands candidates}
                \resumeItem{\textbf{Winners} of 24-hour \textbf{Project Challenge 2019} organized by Xcelerator at REVA University Bangalore Division in 2019}
                \resumeItem{Runner-Up position in the \textbf{Smart India Hackathon Phase-2 Regional Level} Program in 2018.}
                \resumeItem{\textbf{Winners} in a football tournament, representing the college at the Cluster Level Sports Meet in 2019.}
                \resumeItem{Recognized with an \textbf{Innovation and Talent Award} from Publicis Sapient for proposing the best solution idea for the Owner Service problem on behalf of the client in 2021.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
